Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-18 paper/sheaf_lics.tex
update admits in Formalization
add summary/conclusion/acknowlegment

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

@@

Overall, with other files containing technical lemmas, the project
contains 6322 lines, and it could be reduced a bit by improving the
way Coq tries to rewrite and apply lemmas automatically. 
%
This constitute a significant amount of work but the part dedicated to
sheaves and sheafification is only 4000, which seems quite reasonable
and is encouraging, because it suggests that homotopy type theory
provides a convenient tool to formalize some part of the theory of
higher topoi.

@@

In our formalization of sheafification defined
Section~\ref{sec:sheafification} (done in 
\texttt{sheaf\_induction.v}), three very technical facts required to
show that $\square$ and $\modal_{n+1}$ are modalities have been
admitted. Nevertheless, we are confident that they can be proven and
have been admitted only by lack of time.
In the proof that diagrams are equal in lemma~\ref{lem:sepiscolim},
the equality of projections is admitted, because if this proof is
obvious on paper, it becomes really technical when formalized.
As a consequence, the fact that $P$ is a colimit of the diagonal
closed diagram is admitted too, but again, this proof should be really
short as it is on paper.

@@

Prove that the Giraud-Rezk-Lurie axiom holds in homotopy type theory,
or at least the particular case we need.

Extend the sheafification to all types, even if non truncated.

Check if Lawvere-Tierney subsumes Grothendieck in higher topos theory.

@@

The authors would like to thank...

@@

% \bibitem[RS13]{sets_in_hott}
% Egbert Rijke and Bas Spitters.
% \newblock Sets in homotopy type theory.
% \newblock 2013.

% \bibitem[{Uni}13]{hottbook}
% {Univalent Foundations Project}.
% \newblock {\em Homotopy Type Theory: Univalent Foundations for Mathematics}.
% \newblock 2013.

% \bibitem[MM92]{maclanemoerdijk}
% Saunders MacLane and Ieke Moerdijk.
% \newblock {\em Sheaves in Geometry and Logic}.
% \newblock Springer-Verlag, 1992.

% \bibitem[HTT]{lurie}
% Jacob Lurie.
% \newblock{\em Higher Topos Theory}.

% \bibitem[AKL]{lumsdaine}
% Peter LeFanu Lumsdaine, Jeremy Avigad and Chris Kapulkin.
% \newblock{\em Homotopy limits in type theory}.

% \end{thebibliography}

>>>>

@@

Overall, with other files containing technical lemmas, the project
contains 6322 lines, and it could be reduced a bit by improving the
way Coq tries to rewrite and apply lemmas automatically. 
%
This constitute a significant amount of work but the part dedicated to
sheaves and sheafification is only 4000, which seems quite reasonable
and is encouraging, because it suggests that homotopy type theory
provides a convenient tool to formalize some part of the theory of
higher topoi. As a comparison, this \TeX\xspace file contains
approximatively 1800 lines.

@@

In our formalization of sheafification defined
Section~\ref{sec:sheafification} (done in 
\texttt{sheaf\_induction.v}), two very technical facts required to
show that $\square$ is a modality have been
admitted. Nevertheless, we are confident that they can be proven and
have been admitted only by lack of time.
In the proof that diagrams are equal in lemma~\ref{lem:sepiscolim},
the equality of projections is admitted, because if this proof is
obvious on paper, it becomes really technical when formalized.
As a consequence, the fact that $P$ is a colimit of the diagonal
closed diagram is admitted too, but again, this proof should be really
short as it is on paper.

@@

In this paper, we defined a way to extend type theory with new
principles, using the already known method in topos theory,
sheafification. Using this method, one an add some principles, like
excluded middle, to type theory, but with computational content, while
doing it with axiom break the extraction of proofs.

Beyond the result, this work allows to illustrate some homotopy type theoritical
techniques, as well as use of proof assistants.

\kq{J'ai un peu copié sur la conclusion de Licata ``Eilenberg MacLane
  spaces''. Si ça pose problème, je changerai.}

In future works, we would like to improve this construction in two
ways:
\begin{itemize}
\item At the moment, the sheafification process only works with
  truncated types. But some classical types in homotopy type theory
  are not truncated, like the circle $\mathbb S^1$. 
  Thus, we plan to extend the sheafification to all types, even if non
  truncated
\item In this work, the Giraud-Rezk-Lurie axiom is admitted. The work
  done in~\cite{lurie} suggests, if we see homotopy type theory as
  higher topos theory, that this axiome could be provable. A
  computer-checked proof of this fact would improve our developpement.
\end{itemize}
Moreover, in topos theory, we know that Lawvere-Tierney subsumes
Grothendieck (\cite{maclanemoerdijk}, section~V.4). Higher Lawvere-Tierney sheaves are
presented here, and higher Grothendieck sheaves in~\cite{lurie} ; we want to
check if this remains true in higher topos theory.

@@

We would like to thank all maintainers of the Coq/HoTT library, who
allowed us to base our formalization on something. We would also like
to thank Bas Spitters for the helpful discussions on the subject.

@@
